---
title: "Interoperability with other scRNA formats"
author: "Yaniv Lubling"
date: "13-02-2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interoperability with other scRNA formats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Metacell supports conversion of the umi matrix object to/from Bioconductor's [SingleCellExperiment](https://bioconductor.org/packages/release/bioc/html/SingleCellExperiment.html) object (a format that can be imported into Seurat). 

## Convert a metacell umi matrix object to a SingleCellExperiment object
The export function creates a SingleCellExperiment object and stores in it the raw umi counts and the metadata data.frame. The function expects the ID of the mat object to be exported:
```{r, eval=FALSE}
sce = scm_export_mat_to_sce(mat_id)
```

If you wish to import the SingleCellExperiment object into Seurat you should also export the log-normalized umi matrix (and then specify the number of umis to scale each cell to before taking the log).
```{r, eval=FALSE}
sce = scm_export_mat_to_sce(mat_id, add_log_counts=TRUE, scale_to=10000)

# To convert the sce into a Seurat object (Seurat v2.0):
# library(Seurat)
# seurat_obj = Convert(sce, to="seurat")
```

## Convert a SingleCellExperiment object into a metacell umi matrix one
The import function expects a SingleCellExperiment object with the raw umi counts in an assay named "counts" (can be changed by the *counts_slot* parameter) and it also imports the cells metadata table:
```{r, eval=FALSE}
mat = scm_import_sce_to_mat(sce)

# The sce object can be converted from a Seurat object:
# libray(Seurat)
# sce = Convert(seurat_obj, "sce")
```
